First steps with blogdown

### 2021-10-12 text/Rmd/first-steps-with-blogdown/index.Rmd
Updated first-steps-with-blogdown

![Dialog box for new project](first-steps-with-blogdown-01.png)

@@

![Dialog box for new project](first-steps-with-blogdown-02.png)

@@

![Dialog box for project type](first-steps-with-blogdown-03.png)

The thid dialog box tells you where to place the new project and you should know what to do from this point.

@@

If you haven't done so already, install the blogdown package. You need to make a choice here. Hugo has a variety of themes that control what features your website will have along with the general appearance of the site.

@@

I tried both yihui/hugo-lithium and wowchemy/starter-academic. There were things I liked a lot about both themes, but there were also things I really hated. By the way, you can easily swithc between themes, but I made a conscious choice: better to restart at Square One. A new theme meant a new project. Again, perhaps overly cautious.

>>>>

![Dialog box for new project](http://www.pmean.com/new-images/21/first-steps-with-blogdown-01.png)

@@

![Dialog box for new project](http://www.pmean.com/new-images/21/first-steps-with-blogdown-02.png)

@@

![Dialog box for project type](http://www.pmean.com/new-images/21/first-steps-with-blogdown-03.png)

The third dialog box tells you where to place the new project and you should know what to do from this point.

@@

If you haven't done so already, install the blogdown package.

If you do not already have hugo installed on your computer, there is a function inside of the blogdown library that will do this for you.

```{}
blogdown::install_hugo()
```

There's no need to reinstall hugo unless your version of hugo is old.

You need to make a choice here. Hugo has a variety of themes that control what features your website will have along with the general appearance of the site.

@@

I tried both yihui/hugo-lithium and wowchemy/starter-academic. There were things I liked a lot about both themes, but there were also things I really hated. By the way, you can easily switch between themes, but I made a conscious choice: better to restart at Square One. A new theme meant a new project. Again, perhaps overly cautious.
